Title Goes Here

### 2019-03-24 analysis/paper/paper.Rmd
resolved
plot of major ornament types

ornaments_count <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`)) %>% 
  group_by(period, Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_lump(as.factor(Categories), n = 5)) %>% 
  mutate(Categories = fct_reorder(Categories, n))

ggplot(transform(ornaments_count,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Categories, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency")
```

>>>>

ornaments_count <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 4))  %>% 
  group_by(period, Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_reorder(Categories, n))

ggplot(transform(ornaments_count,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Categories, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "") +
  theme_minimal(base_size = 14)
```
